---
title: "Developing Data Products Course Project"
author: "Joel Modisette"
date: "11/17/2021"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Introduction

This presentation is the Course Project for the Developing Data Products Coursera course.

The Shiny application is available at:     
<https://jdmodisette.shinyapps.io/finalproject/>.

The Shiny app source code and this presentation source code is available at:     
[joelmodisette github](<https://github.com/joelmodisette/datasciencecoursera/tree/master/Course9_Dev_Data_Products>)

The project objective is to provide an R Shiny app that allows the user to explore the MITRE ATT&CK Cybersecurity Threat Intelligence database.

## Overview

- The application is written in Shiny, a web application framework for R.
- server.R contains the backend of this Shiny web application.
- ui.R contains the user-interface elements.
- Global.R downloads and prepares v10.1 datasets from https://attack.mitre.org.
- The application is hosted on Rstudio's shiny server.

The application allows the user to explore how cyber threat actors use techniques for exploitation. The techniques relate to general tactics which explain how a cyber actor is attacking. All data comes from the MITRE ATT&CK v10.1 Cyber Threat Landscape. ATT&CK V10.1 was published in November 2021. The datasets are pulled from the MITRE website.

## How the App works:

All information is contained in one main panel.

- Select a Cyber Threat Actor from the drop down menu.
- A SanKey graph presents how the specified actor uses known MITRE Techniques.
- The MITRE Techniques flow into the known MITRE Tactics, also known as the Cyber Kill Chain.
- You may interact with the graph by moving around the nodes.
- A table is generated below the graph. It provides a complete description of each actor, technique and tactic in the displayed graph.

## Sample R Shiny App View

```{r sanKey, echo = FALSE, warning=FALSE, message=FALSE}
library(dplyr)
library(networkD3)
library(tidyr)

nodes <- read.csv("nodes.csv")
links <- read.csv("links.csv")

sankeyNetwork(Links = links, 
              Nodes = nodes, 
              Source = 'source',  
              Target = 'target',  
              Value = 'value',  
              NodeID = 'name')

```
